Brother, Can You Spare a Manufacturing Job? How Voters React to Deindustrialization

### 2021-12-09 Final Draft/Final Draft.Rmd
updates

% AER-Article.tex for AEA last revised 22 June 2011
\documentclass[AER]{AEA}

% The mathtime package uses a Times font instead of Computer Modern.
% Uncomment the line below if you wish to use the mathtime package:
%\usepackage[cmbold]{mathtime}
% Note that miktex, by default, configures the mathtime package to use commercial fonts
% which you may not have. If you would like to use mathtime but you are seeing error
% messages about missing fonts (mtex.pfb, mtsy.pfb, or rmtmi.pfb) then please see
% the technical support document at http://www.aeaweb.org/templates/technical_support.pdf
% for instructions on fixing this problem.

% Note: you may use either harvard or natbib (but not both) to provide a wider
% variety of citation commands than latex supports natively. See below.

% Uncomment the next line to use the natbib package with bibtex
\usepackage{natbib}

% Uncomment the next line to use the harvard package with bibtex
%\usepackage[abbr]{harvard}

% This command determines the leading (vertical space between lines) in draft mode
% with 1.5 corresponding to "double" spacing.
\draftSpacing{1.5}

% For Pandoc highlighting needs

% Pandoc citation processing

\usepackage{hyperref}

\begin{document}

\title{Untitled}
\shortTitle{A shorter title}
% \author{Author1 and Author2\thanks{Surname1: affiliation1, address1, email1.
% Surname2: affiliation2, address2, email2. Acknowledgements}}

\author{
  Alice Anonymous\\
  Bob Security\thanks{
  Anonymous: Some Institute of Technology, \href{mailto:alice@example.com}{alice@example.com}.
  Security: Another University, \href{mailto:bob@example.com}{bob@example.com}.
  Acknowledgements
}
}

\date{\today}
\pubMonth{12}
\pubYear{2021}
\pubVolume{1}
\pubIssue{1}
\JEL{A10, A11}
\Keywords{first keyword, second keyword}

\begin{abstract}
Abstract goes here
\end{abstract}

\maketitle

@@

References here (manual or bibTeX). If you are using bibTeX, add your
bib file name in place of BibFile in the bibliography command. \% Remove
or comment out the next two lines if you are not using bibtex.

\bibliographystyle{aea}
\bibliography{references}

\% The appendix command is issued once, prior to all appendices, if any.
\appendix

@@

\end{document}

>>>>

---
title: "Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization"
short: ""
journal: "" # AER, AEJ, PP, JEL
month: "`r format(Sys.Date(), '%m')`"
year: "`r format(Sys.Date(), '%Y')`"
vol: 1
issue: 1
jel:
  - 
  -
keywords:
  - 
  - 
author:
  - name: Catherine Darin
    firstname: Catherine
    surname: Darin
    email: cdarin@hks.harvard.edu
    affiliation: Harvard University
  - name: Zagreb Mukerjee
    firstname: Zagreb
    surname: Mukergee
    email: zagrebmukerjee@fas.harvard.edu
    affiliation: Harvard University
acknowledgements: 
abstract: |
  What led to Donald Trump's surprising 2016 election victory? This paper examines the potential contribution of deindustrialization. Counties differ by exposure to manufacturing, which we use in an instrumental-variable approach to identify the effect of manufacturing job loss on change in Democratic vote share. We find that Democratic vote share falls in counties with high manufacturing job loss since 2004. Disaggregating this result by race shows that the Democratic vote share fell where layoffs affected white populations, and rose where layoffs affected nonwhites. This suggests a racial component to how voters process economic hardship.
output: rticles::aea_article
---

@@

References here (manual or bibTeX). If you are using bibTeX, add your bib file
name in place of BibFile in the bibliography command.
% Remove or comment out the next two lines if you are not using bibtex.
\bibliographystyle{aea}
\bibliography{references}

% The appendix command is issued once, prior to all appendices, if any.
\appendix

@@

### 2021-12-09 Final Draft/Final-Draft.tex
updates

% AER-Article.tex for AEA last revised 22 June 2011
\documentclass[AER]{AEA}

@@

\title{Untitled}
\shortTitle{A shorter title}
% \author{Author1 and Author2\thanks{Surname1: affiliation1, address1, email1.
% Surname2: affiliation2, address2, email2. Acknowledgements}}

\author{
  Alice Anonymous\\
  Bob Security\thanks{
  Anonymous: Some Institute of Technology, \href{mailto:alice@example.com}{alice@example.com}.
  Security: Another University, \href{mailto:bob@example.com}{bob@example.com}.
  Acknowledgements
}
}

\date{\today}
\pubMonth{12}
\pubYear{2021}
\pubVolume{1}
\pubIssue{1}
\JEL{A10, A11}
\Keywords{first keyword, second keyword}

\begin{abstract}
Abstract goes here
\end{abstract}

>>>>

% AER-Article.tex for AEA last revised 22 June 2011
\documentclass[]{AEA}

@@

\title{Brother, Can You Spare a Manufacturing Job? How Voters React to
Deindustrialization}

% \author{Author1 and Author2\thanks{Surname1: affiliation1, address1, email1.
% Surname2: affiliation2, address2, email2. Acknowledgements}}

\author{
  Catherine Darin\\
  Zagreb Mukerjee\thanks{
  Darin: Harvard University, \href{mailto:cdarin@hks.harvard.edu}{cdarin@hks.harvard.edu}.
  Mukergee: Harvard University, \href{mailto:zagrebmukerjee@fas.harvard.edu}{zagrebmukerjee@fas.harvard.edu}.
}
}

\date{\today}
\pubMonth{12}
\pubYear{2021}
\pubVolume{1}
\pubIssue{1}
\JEL{, }
\Keywords{, }

\begin{abstract}
What led to Donald Trump's surprising 2016 election victory? This paper
examines the potential contribution of deindustrialization. Counties
differ by exposure to manufacturing, which we use in an
instrumental-variable approach to identify the effect of manufacturing
job loss on change in Democratic vote share. We find that Democratic
vote share falls in counties with high manufacturing job loss since
2004. Disaggregating this result by race shows that the Democratic vote
share fell where layoffs affected white populations, and rose where
layoffs affected nonwhites. This suggests a racial component to how
voters process economic hardship.
\end{abstract}
